\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{array}
\usepackage{graphicx}

\begin{document}

\begin{center}
\textbf{BB-1} \\
\textbf{(Under Section 10.3.1-a)} \\
\textbf{APPLICATION FORM FOR NOTICE/PERMISSION TO BUILD} \\
\textit{For Office Use Only} \\
Application No. \rule{5cm}{0.15mm} \\
Date: \rule{0.5cm}{0.15mm} / \rule{0.5cm}{0.15mm} / \rule{0.5cm}{0.15mm}
\end{center}

To \\
The MO (P) \\
Sir/Madam, \\

I/We hereby apply for permission to execute the work of erecting / re-erecting a building of the following description on Plot No. \rule{5cm}{0.15mm} of Scheme \rule{5cm}{0.15mm}. \\

The following papers accompany this application:- \\
\begin{enumerate}
    \item Title Documents: \hfill \hspace{1cm} $\square$
    \item Site Plan (four copies): \hfill \hspace{1cm} $\square$
    \item Block plan of the site (four copies): \hfill \hspace{1cm} $\square$
    \item Building plan (four copies): \hfill \hspace{1cm} $\square$
    \item Specifications (in duplicate): \hfill \hspace{1cm} $\square$
\end{enumerate}

We undertake that construction will be done as per approved plans and in accordance with Building Bye laws. \\

\begin{tabular}{|l|l|}
\hline
Son of & \rule{8cm}{0.15mm} \\
Daughter of & \\
Wife of & \\
Widow of & \\
\hline
\end{tabular}

\begin{tabular}{|l|l|}
\hline
\textbf{Correspondence} & \\
Address: & \rule{8cm}{0.15mm} \\
Phone: & \rule{8cm}{0.15mm} \\
Date: & \rule{8cm}{0.15mm} \\
\hline
\end{tabular}

\begin{tabular}{|l|l|}
\hline
\textbf{Name of Registered Architect:} & \rule{8cm}{0.15mm} \\
\textbf{Registration No. of Registered Architect:} & \rule{8cm}{0.15mm} \\
Address: & \rule{8cm}{0.15mm} \\
Phone: & \rule{8cm}{0.15mm} \\
\hline
\end{tabular}

\begin{tabular}{|l|}
\hline
\textbf{Signature of applicant/ builder} \rule{8cm}{0.15mm} \\
\hline
\textbf{Signature of Registered Architect} \rule{8cm}{0.15mm} \\
\hline
\end{tabular}

\end{document}

\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{amsmath}

\begin{document}

\begin{center}
\textbf{BB-2} \\
(Under Section 10.3.1-a) \\
\textbf{APPLICATION FORM FOR NOTICE/PERMISSION TO BUILD MULTI-STOREYED BUILDINGS \& BUILDINGS OF PUBLIC ASSEMBLY}
\end{center}

\textbf{To} \\
The MO (P) \\
Sir/Madam, \\

I/We hereby apply for permission to execute the work of erecting/re-erecting a building of the following description on Plot No. \dotfill of Scheme \dotfill

The following papers accompany this application:
\begin{enumerate}
    \item Site Plan \hfill Sheets (in triplicate) \hspace{1cm} $\square$
    \item Building Plan \hfill Sheets (in triplicate) \hspace{1cm} $\square$
    \item Specifications \hfill Sheets (in duplicate) \hspace{1cm} $\square$
    \item Title Documents \hfill \hspace{4.5cm} $\square$
    \item Structure Stability Certificate \hspace{1.5cm} $\square$
    \item An Undertaking regarding damages. \hspace{1.5cm} $\square$
\end{enumerate}

We, the undersigned, hereby undertake that the design, construction and supervision shall be in accordance with the provisions of the Building Bye laws.

\begin{tabular}{l l}
\textbf{Consulting Engineer} & \textbf{Registered Architect} \\
PEC Registration No: \dotfill & PCATP Registration \\
& No: \dotfill \\
\end{tabular}

\begin{tabular}{l l}
\textbf{Owner} & \\
Address: \dotfill & Address: \dotfill \\
\dotfill & \dotfill \\
\dotfill & \dotfill \\
\end{tabular}

\end{document}

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\begin{document}

\begin{center}
\textbf{BB-3} \\
(to be submitted in duplicate with notice BB-1 or BB-2) \\
\textbf{FORM OF SPECIFICATIONS}
\end{center}

\begin{enumerate}
    \item[(A)] The materials and methods of construction to be used for external walls, party walls, foundations, roofs, staircases, bath rooms, fire places, chimneys, and damp proof course shall be as per requirements of building code.
    \item[(B)] The purpose or purposes for which the building is intended to be used
    \item[(C)] The number of Toilets, privies and urinals to be provided.
    \item[(D)] The manner in which the drainage of the premises will be disposed of
    \item[(E)] The number of persons likely to occupy the building.
    \item[(F)] The number of storeys, the building will consist of.
    \item[(G)] Whether the site has been built upon before or not. If so the date when the previous building ceased to be fit for occupation and the date when sanction was previously given for erection or re-erection of the building \& the property number.
    \item[(H)] A description of the alterations or additions proposed.
    \item[(I)] The date of sanction of the previous application, the plans and specifications of which are relied upon for obviating the need to submit full plans and specifications of whole building.
\end{enumerate}

\vspace{1cm}
\begin{center}
\dots \dots \dots \dots \dots \dots \dots \dots \dots \dots \dots \dots \dots \dots \\
Signature of the Applicant/ Builder \\
Date: / /
\end{center}

\end{document}

\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{array}

\begin{document}

\begin{center}
\textbf{BB-4} \\
(to be submitted in duplicate with notice BB-1 or BB-2) \\
\textbf{DETAILS OF BUILDING SPECIFICATIONS}
\end{center}

\begin{enumerate}
    \item The material \& methods of construction to be used for foundations, damp proof course, external walls, internal walls, roof, staircase and floors, etc.
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Foundations} & \\
        \hline
        \textbf{DPC} & \\
        \hline
        \textbf{External and Internal Walls} & \\
        \hline
        \textbf{Roof} & \\
        & \begin{itemize}
            \item RCC slab
            \item RCB roof
            \item Steel girder
            \item Pre-cast slabs and pre-stressed girders.
            \item Second class roof consisting of bullies, rafters and tiles.
        \end{itemize} \\
        \hline
        \textbf{Staircase} & \\
        \hline
        \textbf{Floors} & \\
        \hline
        \textbf{Joinery Work} & \\
        & \begin{itemize}
            \item Wooden doors, windows and CSW.
            \item Steel doors, windows and CSW.
        \end{itemize} \\
        \hline
        \textbf{Beams/Columns} & \\
        \hline
    \end{tabular}
    \item The purpose for which the building is intended to be used.
    \begin{tabular}{|l|l|}
        \hline
         & Residential / Commercial / Industrial / Other. \\
        \hline
    \end{tabular}
    \item The number of latrine, bath and urinals to be provided. \\
    \hline
\end{enumerate}

\end{document}

\documentclass{article}
\usepackage{array}

\begin{document}

\begin{tabular}{|m{0.1\textwidth}|m{0.8\textwidth}|}
\hline
4. & The manner in which drainage / sewerage of premises shall be disposed off. \\
\hline
5. & The total area of openings. \\
\hline
6. & The number of stories of the building. \\
\hline
7. & Whether the site has been built upon before or not? \newline Building Plan No. \dotfill \newline Dated: \dotfill \newline If yes then give the date when sanction was previously given for erection / re-erection of building. \\
\hline
8. & Other \\
\hline
\multicolumn{2}{|c|}{Approving Authority: \dotfill \newline (attested copy of sanctioned plan enclosed).} \\
\hline
\multicolumn{2}{|c|}{\dotfill} \\
\hline
\multicolumn{2}{|c|}{\textbf{Signature of Designer} \hspace*{\fill} \textbf{Signature of Builder}} \\
\hline
\end{tabular}

\end{document}

