\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{array}

\begin{document}

\begin{center}
\textbf{GOVERNMENT OF PUNJAB} \\
\textbf{PUNJAB LAND RECORDS AUTHORITY} \\
\textbf{BOARD OF REVENUE, LAHORE.}
\end{center}

\begin{center}
\textbf{DECLARATION OF INCOME AND ASSETS} \\
Financial Year Ending on 30th June \underline{\hspace{2cm}}
\end{center}

\begin{enumerate}
    \item \textbf{Name} \hspace{1cm} \rule{10cm}{0.5pt}
    \item \textbf{Basic Pay Scale} \hspace{1cm} \framebox[1cm][c]{} \hspace{1cm} \textbf{Occupation Group/} \\
    \textbf{Service/Department} \hspace{1cm} \rule{10cm}{0.5pt}
    \item \textbf{Present Position Held} \hspace{1cm} \rule{10cm}{0.5pt} \\
    \textbf{Present Residential Address} \hspace{1cm} \rule{10cm}{0.5pt} \\
    \textbf{Phone (R)} \hspace{1cm} \rule{5cm}{0.5pt} \hspace{1cm} \textbf{Mobile} \hspace{1cm} \rule{5cm}{0.5pt} \\
    \item \textbf{Income} \\
    (During the financial year) \\
    \textbf{Salary} \hspace{1cm} Rs. \hspace{1cm} \rule{7cm}{0.5pt} \\
    \textbf{Other sources (dividend, profit, prize money, gift, loan etc.)} \\
    Rs. \hspace{1cm} \rule{7cm}{0.5pt} \hspace{1cm} \textbf{Total} \hspace{1cm} Rs. \hspace{1cm} \rule{7cm}{0.5pt} \\
    \textbf{Rental income} \hspace{1cm} Rs. \hspace{1cm} \rule{7cm}{0.5pt} \hspace{1cm} \textbf{Agrl income} \hspace{1cm} Rs. \hspace{1cm} \rule{7cm}{0.5pt} \\
    \item \textbf{Expenses} \\
    (Approx.) \\
    \textbf{Utilities (Electricity, Gas, Telephone etc.)} \hspace{1cm} Rs. \hspace{1cm} \rule{7cm}{0.5pt} \\
    \textbf{Total Household expenses} \hspace{1cm} Rs. \hspace{1cm} \rule{7cm}{0.5pt} \\
    \item \textbf{Private Foreign Traveling} \\
    (Self, Spouse \& Children) \\
    During F.Y. \underline{\hspace{5cm}} \\
    \textbf{Country/Countries visited} \hspace{1cm} \rule{10cm}{0.5pt} \\
    \textbf{Period of stay} \hspace{1cm} From \underline{\hspace{2cm}} to \underline{\hspace{2cm}} \\
    \textbf{Approx. expenses} \hspace{1cm} Rs. \hspace{1cm} \rule{7cm}{0.5pt} \\
    \item \textbf{Children's Education} \\
    (inland \& abroad) \\
    \textbf{Name(s) of children} \hspace{1cm} \rule{10cm}{0.5pt} \\
    \rule{10cm}{0.5pt} \\
    \rule{10cm}{0.5pt} \\
    \textbf{Educational institutions attended during F.Y.} \\
    \rule{10cm}{0.5pt} \\
    \rule{10cm}{0.5pt} \\
    \rule{10cm}{0.5pt} \\
    \item \textbf{Club Membership} \\
    \textbf{Name of Club(s)} \hspace{1cm} \rule{10cm}{0.5pt} \\
    \textbf{Membership No.} \hspace{1cm} \rule{10cm}{0.5pt}
\end{enumerate}
\begin{center}
1/4
\end{center}
\end{document}

\documentclass{article}
\usepackage{array}
\begin{document}
\begin{center}
\textbf{ASSETS \& LIABILITIES}
\end{center}

\vspace{0.5cm}
9. \textbf{Immoveable Assets} (Agri \& Non-Agri lands, House properties, Commercial \& Industrial properties, Open plots of all types)

\begin{tabular}{|l|l|l|}
\hline
\textbf{Identification \& nature of Asset(s)} & \textbf{Mode of acquisition/year} & \textbf{Cost of acquisition} \\
\hline
a) &  &  \\
\hline
b) &  &  \\
\hline
c) &  &  \\
\hline
d) &  &  \\
\hline
e) &  &  \\
\hline
f) &  &  \\
\hline
g) &  &  \\
\hline
h) &  &  \\
\hline
i) &  &  \\
\hline
j) &  &  \\
\hline
k) &  &  \\
\hline
l) &  &  \\
\hline
m) &  &  \\
\hline
\end{tabular}

\vspace{0.5cm}
10. \textbf{Moveable Assets} (Cash in hand, Motor vehicles, Jewellery, Household items, Equipment, Business capital etc.)

\begin{tabular}{|l|l|l|}
\hline
\textbf{Identification \& nature of Asset(s)} & \textbf{Mode of acquisition/year} & \textbf{Cost of acquisition} \\
\hline
a) &  &  \\
\hline
b) &  &  \\
\hline
c) &  &  \\
\hline
d) &  &  \\
\hline
e) &  &  \\
\hline
f) &  &  \\
\hline
g) &  &  \\
\hline
h) &  &  \\
\hline
i) &  &  \\
\hline
j) &  &  \\
\hline
k) &  &  \\
\hline
l) &  &  \\
\hline
m) &  &  \\
\hline
\end{tabular}

\vspace{0.5cm}
11. \textbf{Assets held as Attorney}

\begin{tabular}{|l|l|l|}
\hline
\textbf{Identification \& nature of Asset(s)} & \textbf{\begin{tabular}[c]{@{}l@{}}Nature of Power of Attorney \\ (Revocable/Irrevocable)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Name \& Address of \\ the Legal Owner\end{tabular}} \\
\hline
a) &  &  \\
\hline
b) &  &  \\
\hline
\end{tabular}

\vspace{0.5cm}
\begin{center}
2/4
\end{center}

\end{document}

\documentclass{article}
\usepackage{array}

\begin{document}

\begin{tabular}{|l|l|}
\hline
\multicolumn{2}{|l|}{12. Assets disposed off during the year} \\
\hline
Identification \& nature of Asset(s) & Date of disposal \\
\hline
a) &  \\
\hline
b) &  \\
\hline
c) &  \\
\hline
d) &  \\
\hline
\multicolumn{2}{|r|}{Amount received as sale proceed (Rs.)} \\
\hline
\end{tabular}

\vspace{0.5cm}

\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{13. Investments (Bonds, Shares, Certificates, deposits/Advances, Loans granted etc.)} \\
\hline
\multicolumn{2}{|l|}{Details of Bonds held} & \multicolumn{2}{l|}{Investments} \\
\hline
Bond No.(s) & Denomination Rs. &  & Rs. \\
\hline
a) &  &  & Rs. \\
\hline
b) &  &  & Rs. \\
\hline
c) &  &  & Rs. \\
\hline
d) &  &  & Rs. \\
\hline
\end{tabular}

\vspace{0.5cm}

\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{5}{|l|}{14. Bank Accounts (Current, Saving, Deposit A/c \& F.C. A/cs)} \\
\hline
A/c No. \& Bank Branch & Year of opening & Main source of deposits & Balance on 30.6. & (Rs.) \\
\hline
a) &  &  &  &  \\
\hline
b) &  &  &  &  \\
\hline
c) &  &  &  &  \\
\hline
d) &  &  &  &  \\
\hline
\end{tabular}

\vspace{0.5cm}

\begin{tabular}{|l|l|}
\hline
15. Total Assets(9$-$14) & Rs. \underline{\hspace{3cm}} \\
\hline
\end{tabular}

\vspace{0.5cm}

\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{16. Liabilities (Departmental/Bank loans, over drafts, Mortgages secured, private loans etc.)} \\
\hline
Outstanding liabilities (A) &  & Liabilities paid off during the year (B) &  \\
\hline
a) Rs. \underline{\hspace{2cm}} &  & Rs. \underline{\hspace{2cm}} &  \\
\hline
b) Rs. \underline{\hspace{2cm}} &  & Rs. \underline{\hspace{2cm}} &  \\
\hline
c) Rs. \underline{\hspace{2cm}} &  & Rs. \underline{\hspace{2cm}} &  \\
\hline
d) Rs. \underline{\hspace{2cm}} &  & Rs. \underline{\hspace{2cm}} &  \\
\hline
\end{tabular}

\vspace{0.5cm}

\begin{tabular}{|l|l|}
\hline
(15$-$16(A)) Net worth & Rs. \underline{\hspace{3cm}} \\
\hline
As on 30.6. \underline{\hspace{3cm}} &  \\
\hline
Net worth declared previously & Rs. \underline{\hspace{3cm}} \\
\hline
As on 30.6. \underline{\hspace{3cm}} &  \\
\hline
Signature \underline{\hspace{5cm}} &  \\
\hline
Name \underline{\hspace{5cm}} &  \\
\hline
Designation \underline{\hspace{5cm}} &  \\
\hline
Name of the Organization/Deptt. \underline{\hspace{5cm}} &  \\
\hline
Place \underline{\hspace{5cm}} &  \\
\hline
Date \underline{\hspace{5cm}} &  \\
\hline
\end{tabular}

\end{document}

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\begin{document}

\begin{center}
\textbf{INSTRUCTIONS}
\end{center}

\begin{enumerate}
    \item If the space provided in the form is found inadequate or some explanation is required, a separate page may be attached/annexed.
    \item All assets should be valued at cost and in the cases of assets acquired through gift name, address of the donor and donees relationship with him is to be declared.
    \item Income declared at Serial 4 must include income earned by the spouse \& children as well.
    \item Information requested must be complete. No column should be left blank. Columns which are not applicable should be crossed.
    \item All assets owned by the officer \& his family members (Family as defined in Rule 3(1)(c) of Conduct Rules 1964) should be declared. Assets acquired by major children dependents \& others where funds have been provided by the officer are also to be declared.
    \item Assets owned partly or acquired on "Hire purchase Agreement" or installment should also be declared.
    \item If any exact figure cannot be inserted an estimated/approx figure may be given.
    \item Sale proceeds of assets disposed off during the relevant financial year must be declared under the head “other sources” (Serial 4).
    \item If there is no change in Assets over the previous year (for which the declaration had been filed) relevant columns (Serial 9, 10, \& 11) may be marked “As Before".
    \item At Serial 11 assets held by others as attorney on behalf of declarant, his spouse or dependent children are also to be declared.
    \item Expenses against utilities (Serial 5) should include bills paid against all meters (Gas \& Electricity installed on the residence) and telephone connections (including Mobile) in use of the officer, spouse \& dependent children.
    \item Notwithstanding the applicability of any other law for the time being in- force, this declaration is being filed under Conduct Rule 1964 and any breach thereof (including concealment of assets or giving wrong information) is punishable under RSO 2000.
\end{enumerate}

\begin{center}
********
\end{center}

\begin{center}
4/4
\end{center}

\end{document}

