\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\begin{document}

\begin{center}
\textbf{POLICE CHARACTER CERTIFICATE}
\end{center}

\textbf{No:} \hspace{2cm}
\textbf{Date:} \hspace{2cm}

\textbf{NAME:} \hspace{2cm} \\
\textbf{S/O, D/O, W/O} \hspace{2cm}

\textbf{CNIC NO.} \hspace{2cm} \underline{\hspace{4cm}} \hspace{1cm} \textbf{Date and Place of Issue:} \hspace{2cm} \underline{\hspace{4cm}} \\

\textbf{PASSPORT NO.} \hspace{2cm} \underline{\hspace{4cm}} \hspace{1cm} \textbf{Date and Place of Issue:} \hspace{2cm} \underline{\hspace{4cm}} \\

\textbf{MOBILE No.} \hspace{2cm} \underline{\hspace{4cm}} \hspace{1cm} \textbf{DATE OF BIRTH:} \hspace{2cm} \underline{\hspace{4cm}} \\

Details of all the temporary/Permanent \& Other residential address in Capital City District Lahore.

\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Status} & \textbf{Residential Address} & \textbf{Concerned} & \multicolumn{2}{c|}{\textbf{Stay Period}} \\
 &  & \textbf{Police Station} & \textbf{From} & \textbf{To} \\ \hline
Permanent &  &  &  &  \\ \hline
Temporary &  &  &  &  \\ \hline
Other &  &  &  &  \\ \hline
Other &  &  &  &  \\ \hline
Other &  &  &  &  \\ \hline
Other &  &  &  &  \\ \hline
\end{tabular}

Purpose of obtaining certificate (visit/immigration/nationality): \underline{\hspace{8cm}} \\
Country name: \underline{\hspace{8cm}} \\
If government servant (department NOC) be attached): \\
I, solemnly declare that all information written in the form is correct and have been completed by myself.

\textbf{Dated} \hspace{2cm} \underline{\hspace{4cm}} \hspace{2cm} \textbf{Signatures of Applicant} \hspace{2cm} \underline{\hspace{4cm}}

\textbf{Note:-Requirements at Submission}

\begin{enumerate}
    \item Application form
    \item 01 snap passport size Fresh photograph (front with light blue or white background un attested)
    \item 01 CNIC Copy (Attested by Lahore Gazetted Officer) (ORIGINAL)
    \item 01 Passport Copy (Attested by Lahore Gazetted Officer) (ORIGINAL)
    \item Affidavit Rs.50 Duly (Attested by Oath Commissioner)
    \item Authority letter (if applicant is abroad)
    \item Requirement at Collection (Show original CNIC)
    \item The Police Character Certificate only submitted with appearance of Applicant is out of Country the form submitted only Blood relation with Authority letter. Authority Letter with the Stamp of Embassy/Consulates/High Commission/Police Station/Notary Public Or Educational Institute or Office/ Organization where applicant working/job.
\end{enumerate}

Clearance Certificate will be issued after one week from the date receipt of this application form. Incharge district security branch: Lahore

\textbf{Contact:} (042-99211544-46) \hspace{1cm} (042-99214847) \hspace{1cm} Rs. 350 (Service + Courier) Charges

\end{document}

